Are rankings of financial analysts useful to investors?

### 2015-03-18 doc/paper/paper-knitr-APS.Rnw
all time for CONS is the median instead of mean

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.

>>>>

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B, C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates. Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.

### 2015-03-18 doc/paper/paper-knitr-APS.tex
all time for CONS is the median instead of mean

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.729\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%). Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).

@@

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.069}\% and 0.441\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 21.729 & 22.216 & 20.478 & 20.715 & 0.102 & 0.101 \\

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates . Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from 2000Q1 until 2009Q4.

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.069 & 0.413 & 15.817 & 15.873 & -0.004 & 0.026 &  290 &  257 & 0.188 & 0.185 \\ 
  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\

@@

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
   \midrule 
All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\

>>>>

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.218\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%). Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).

@@

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.032}\% and 0.441\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
  \default{} & 21.218 & 21.729 & 19.742 & 20.014 & 0.107 & 0.106 \\

@@

\begin{table}[hp]
  \caption{Trading strategies performance: entire period}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B, C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates. Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking. The trading period goes from 2000Q1 until 2009Q4.

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & -0.032 & 0.478 & 15.827 & 15.860 & -0.002 & 0.030 &  290 &  257 & 0.189 & 0.187 \\ 
  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\

@@

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.891 & 0.251 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.581 & 0.234 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.604 & 0.431 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 8.217 & 0.865 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -5.999 & -0.435 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -3.806 & -0.233 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
   \midrule 
All period & -3.032 & -0.182 & -0.032 & -0.002 & -0.005 & -0.000 & 0.441 & 0.028 \\
